---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# comorbidPRS

<!-- badges: start -->
[![GitHub tag](https://img.shields.io/github/v/tag/VP-biostat/comorbidPRS.svg?label=latest%20version)](https://github.com/VP-biostat/comorbidPRS)
<!-- badges: end -->

comorbidPRS is a tool for analysing an already computed Polygenic Score (PGS, also named PRS/GRS for binary outcomes) distribution to investigate shared genetic aetiology in multiple conditions.

comorbidPRS is under GPL-3 license, and is freely available for download. 

## Prerequisite
* R version 3.5 or higher with the following packages:
    + stats 
    + utils
    + ggplot2 

## Installation

You can install the development version of comorbidPRS from [GitHub](https://github.com/VP-biostat/comorbidPRS) with:

``` r
# install.packages("devtools")
devtools::install_github("VP-biostat/comorbidPRS")
```

## Example

### Building an Association Table

This is a basic example which shows you how to do basic association with the example dataset:

```{r example, results = 'hide', warning = FALSE}
library(comorbidPRS)

# use the demo dataset
dataset <- comorbidData
# NOTE: The dataset must have at least 3 different columns:
# - an ID column (the first one)
# - a PGS column (must be numeric, by default it is the column named "SCORESUM" or the second column if "SCORESUM" is not present)
# - a Phenotype column, can be factors, numbers or characters

# do an association of one PGS with one Phenotype
result_1 <- assoc(dataset, prs_col = "t2d_PGS", phenotype_col = "t2d")
```
```{r result_1, echo = FALSE}
knitr::kable(result_1)
```
```{r example multiple assoc, results = 'hide'}
# do multiple associations
assoc <- expand.grid(c("t2d_PGS", "ldl_PGS"), c("ethnicity","brc","t2d","log_ldl","sbp_cat"))
result_2 <- multiassoc(df = dataset, assoc_table = assoc, covar = c("age", "sex", "gen_array"))
```
```{r result_2, echo = FALSE}
knitr::kable(result_2)
```


### Examples of plot

```{r densityplot}
densityplot(dataset, prs_col = "ldl_PGS", phenotype_col = "sbp_cat")
```

```{r assocplot}
# show multiple associations in a plot
assoplot <- assocplot(score_table = result_2)
assoplot$continuous_phenotype
assoplot$discrete_phenotype
```
NOTE: The score_table should have the assoc() output format

```{r centileplot}
centileplot(dataset, prs_col = "brc_PGS", phenotype_col = "brc")
```

As those graphical functions use ggplot2, you can fully customize your plot:
```{r centileplot-and-ggplot}
library(ggplot2)
centileplot(dataset, prs_col = "t2d_PGS", phenotype_col = "t2d") + 
  scale_color_gradient(low = "green", high = "red")
```

```{r decileplot, warning=FALSE}
decileboxplot(dataset, prs_col = "ldl_PGS", phenotype_col = "ldl")
```

## Citation 
If you use comorbidPRS in any published work, please cite the following manuscript:

```{r citation, echo = FALSE, results = 'asis', warning = FALSE}
print(citation("comorbidPRS"), "html")
```
