---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# comorbidPRS

<!-- badges: start -->
[![GitHub tag](https://img.shields.io/github/v/tag/VP-biostat/comorbidPRS.svg?label=latest%20version)](https://github.com/VP-biostat/comorbidPRS)
<!-- badges: end -->

comorbidPRS is a tool for analysing an already computed PRS distribution to investigate shared aetiology in multiple conditions.

comorbidPRS is under GPL-3 license, and is freely available for download. 

## Prerequisite
stats 
utils
ggplot2 
R version 3.5 or higher 

## Installation

You can install the development version of comorbidPRS from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("VP-biostat/comorbidPRS")
```

## Example

This is a basic example which shows you how to do basic association with the example dataset:

```{r example, echo = FALSE}
library(comorbidPRS)

#use the demo dataset
dataset <- comorbidExample

#do an association of one PRS with one Phenotype
result_1 <- assoc(dataset, prs_col = "PRS_1", phenotype_col = "Phenotype_1")
print(result_1)
```
```{r example multiple assoc, echo = FALSE}
#do multiple associations
assoc <- expand.grid(c("PRS_1", "PRS_2"), c("Phenotype_1", "Phenotype_2", "Phenotype_3", "Phenotype_4"))
result_2 <- multiassoc(df = dataset, assoc_table = assoc, covar = c("Age", "Sex", "Covariate"))
print(result_2)
```

Examples of plot: 

```{r decileplot, echo = FALSE}
decileboxplot(dataset, prs_col = "PRS_1", phenotype_col = "Phenotype_1")
```

```{r densityplot, echo = FALSE}
comorbidPRS::densityplot(dataset, prs_col = "PRS_1", phenotype_col = "Phenotype_2")
```

```{r centileplot, echo = FALSE}
comorbidPRS::centileplot(dataset, prs_col = "PRS_2", phenotype_col = "Phenotype_3")
```

```{r orplot, echo = FALSE}
#show multiple associations in a plot
comorbidPRS::orplot(score_table = result_2)
```

## Citation 
If you use comorbidPRS in any published work, please cite the following manuscript:

```{r citation, echo=FALSE, results = 'asis'}
print(citation('comorbidPRS'), 'html')
```
