---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# comorbidPRS

<!-- badges: start -->
[![GitHub tag](https://img.shields.io/github/v/tag/VP-biostat/comorbidPRS.svg?label=latest%20version)](https://github.com/VP-biostat/comorbidPRS)
<!-- badges: end -->

comorbidPRS is a tool for analysing an already computed PRS distribution to investigate shared aetiology in multiple conditions.

comorbidPRS is under GPL-3 license, and is freely available for download. 

## Prerequisite
* R version 3.5 or higher with the following packages:
    + stats 
    + utils
    + ggplot2 

## Installation

You can install the development version of comorbidPRS from [GitHub](https://github.com/VP-biostat/comorbidPRS) with:

``` r
# install.packages("devtools")
devtools::install_github("VP-biostat/comorbidPRS")
```

## Example

### Building an Association Table

This is a basic example which shows you how to do basic association with the example dataset:

```{r example, results = 'hide'}
library(comorbidPRS)

# use the demo dataset
dataset <- comorbidExample
# NOTE: The dataset must have at least 3 different columns:
# - an ID column (the first one)
# - a PRS column (must be numeric, by default it is the column named "SCORESUM" or the second column if "SCORESUM" is not present)
# - a Phenotype column, can be factors, numbers or characters

# do an association of one PRS with one Phenotype
result_1 <- assoc(dataset, prs_col = "PRS_1", phenotype_col = "Phenotype_1")
```
```{r result_1, echo = FALSE}
knitr::kable(result_1)
```
```{r example multiple assoc, results = 'hide'}
# do multiple associations
assoc <- expand.grid(c("PRS_1", "PRS_2"), c("Phenotype_1", "Phenotype_2", "Phenotype_3", "Phenotype_4"))
result_2 <- multiassoc(df = dataset, assoc_table = assoc, covar = c("Age", "Sex", "Covariate"))
```
```{r result_2, echo = FALSE}
knitr::kable(result_2)
```


### Examples of plot

```{r densityplot}
densityplot(dataset, prs_col = "PRS_1", phenotype_col = "Phenotype_2")
```

```{r orplot}
# show multiple associations in a plot
orplot(score_table = result_2)
```
NOTE: The score_table should have the assoc() output format

```{r centileplot}
centileplot(dataset, prs_col = "PRS_2", phenotype_col = "Phenotype_3")
```

As those graphical functions use ggplot2, you can fully customize your plot:
```{r centileplot and ggplot}
library(ggplot2)
centileplot(dataset, prs_col = "PRS_1", phenotype_col = "Phenotype_2") + 
  scale_color_gradient(low = "green", high = "red")
```

```{r decileplot}
decileboxplot(dataset, prs_col = "PRS_1", phenotype_col = "Phenotype_1")
```

## Citation 
If you use comorbidPRS in any published work, please cite the following manuscript:

```{r citation, echo = FALSE, results = 'asis', warning = FALSE}
print(citation("comorbidPRS"), "html")
```
